Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
brevity and clarity
avoids passive voice... rewrites interpolation table sentence a bit.

In this work $Q_g$ is set equal to $\gamma Q_f$, where $\gamma$ is a factor
representing heat dissipation by gamma and neutron irradiation in the moderator.

Group constants are generated by the modeler with either Serpent
\cite{leppanen_serpent_2015} or SCALE \cite{dehart_reactor_2011}. Group constant
temperature dependence is implemented via interpolation tables, which must be
constructed separately for fuel and moderator regions. For this report,
SCALE-generated group constants were used. To generate the group constants, an
infinite square pitch lattice of cylindrical fuel channels surrounded by
graphite was used, maintaining a fuel fraction of .225 to be consistent with the
\gls{MSRE}. Subsequently, a critical buckling calculation was applied. The SCALE
input files used for generating the group constants can be found in the
\code{io/msre\_conc\_cuboid\_lattice} directory of the
\url{github.com/arfc/scale_io} repository.

>>>>

In this work, $Q_g = \gamma Q_f$, where $\gamma$ is a factor
representing heat dissipation by gamma and neutron irradiation in the moderator.

Group constants are generated by the modeler with either Serpent
\cite{leppanen_serpent_2015} or SCALE \cite{dehart_reactor_2011}. Moltres 
interpolates group constant temperature dependence from prepared tables, which must be
constructed separately for fuel and moderator regions. For this report,
SCALE-generated group constants were used. To generate the group constants, an
infinite square pitch lattice of cylindrical fuel channels surrounded by
graphite was used, maintaining a fuel fraction of .225 to be consistent with the
\gls{MSRE}. Subsequently, a critical buckling calculation was applied. The SCALE
input files used for generating the group constants can be found in the
\code{io/msre\_conc\_cuboid\_lattice} directory of the
\url{github.com/arfc/scale_io} repository.
